Capon Beamforming Applied on Moving Objects - An Analysis of Local Shift-Invariance

### 2013-10-31 HRUIofMovingObjects/jrnl_article.tex
some changes to moving objects paper

\section{Local Shift Invariance of the Capon Beamformer}

@@

\section{Oversampling on Transmitt}

@@

\section{Oversampling by Phase Rotation}

@@

\section{Oversampling by Parallel Recieve Lines}
\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{\img capon_L=32_K=1_d=001_2MLA_and_2x_microsteering_correct_pitch.eps}
\label{fig:image_capon_bs}
\end{figure}

\section{In-vitro Images}
Acquire channel data from a phantom containing point wire targets and cysts while moving the probe laterally. Confirm the improved shift-invariance when using phase rotation.

\section{In-Vivo Images}
Investigate if phase rotation improves contrast in in-vivo images of the heart.

\section{Results}\label{sec:res}
Make plot of contrast between two areas in a simulation for different values of $L$. Make the same plot for different number of rx beams. Do the same for an in-vivo image. The rational being that contrast is also improved by denser rx-sampling not just shift-invariance.

>>>>

\section{Local Lateral Shift-Invariance of the Capon Beamformer}

@@

\section{Methods}

\subsection{Oversampling on Transmitt}

@@

\subsection{Oversampling by Phase Rotation}

@@

\subsection{Oversampling by Parallel Recieve Lines}
\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{\img capon_L=32_K=1_d=001_2MLA_and_2x_microsteering_correct_pitch.eps}
\label{fig:image_capon_bs}
\end{figure}

\section{Results}\label{sec:res}

Make plot of contrast between two areas in a simulation for different values of $L$. Make the same plot for different number of rx beams. Do the same for an in-vivo image. The rational being that contrast is also improved by denser rx-sampling not just shift-invariance.

\subsection{In-vitro Images}
Acquire channel data from a phantom containing point wire targets and cysts while moving the probe laterally. Confirm the improved shift-invariance when using phase rotation.

\subsection{In-Vivo Images}
Investigate if phase rotation improves contrast in in-vivo images of the heart.
